Irt plot extra

### 2022-03-30 manuscript.Rmd
Figure Captions corrected

---
title             : "_Light Exposure behaviour Assessment (LEBA)_: Development of a novel instrument to capture light exposure-related behaviours"
shorttitle        : "LEBA"

@@

```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern', out.height='100%', out.width='250%'}
knitr::include_graphics('Figures/Figure2.png')

@@

```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern', out.height='100%', out.width='250%'}
knitr::include_graphics('Figures/Figure3.png')

@@

```{r Testinfo, fig.env = "sidewaysfigure", fig.cap="Test information curves for the five factors of LEBA: (a) wearing blue light filters (b) spending time outdoors (c) using phone and smartwatchin bed (d) using light before bedtime (e) using light in the morning andduring daytime. Along x-axis we plotted the underlying latent trait continumm for each factor. Along y-axis we plotted how much information a particular factor is caring across its latent trait continuum", warning=FALSE, out.width="100%", out.height="120%"}

>>>>

---
title             : "_Light Exposure Behaviour Assessment (LEBA)_: Development of a novel instrument to capture light exposure-related behaviours"
shorttitle        : "LEBA"

@@

```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern observed in the large-scale survey for item 01-24. All items violated normality assumption', out.height='100%', out.width='250%'}
knitr::include_graphics('Figures/Figure2.png')

@@

```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern observed in the large-scale survey for item 25-48. All items violated normality assumption', out.height='100%', out.width='250%'}
knitr::include_graphics('Figures/Figure3.png')

@@

```{r Testinfo, fig.env = "sidewaysfigure", fig.cap="Test information curves for the five factors of LEBA: (a) wearing blue light filters (b) spending time outdoors (c) using phone and smart-watch in bed (d) using light before bedtime (e) using light in the morning and during daytime. Along x-axis we plotted the underlying latent trait continuum for each factor. Along y-axis we plotted how much information a particular factor is caring across its latent trait continuum", warning=FALSE, out.width="100%", out.height="120%"}
